Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
Remove discussion of bias-corrected ATE point estimates from empirics
The bias-corrected point estimates are not inherently interesting: the uncorrected
estimates are. Consequently, this commit removes detailed discussion of the uncorrected
point estimates from the main text of the paper.

Results from the two robust procedures are similar to each other but greatly
differ from the original estimates. The estimated ATEs are as high as --3.795
from CCT and --3.800 from the bootstrap. Both are significantly different from
zero, though the confidence intervals are also very wide, which is likely to be
due to the much smaller bandwidths used relative to the other estimators
($h=3.888$, $b=6.807$).

@@

The two robust procedures are again very similar to each other and give slightly
larger point estimates in both panels. In Panel A, the ATE increases from 0.030
to 0.055 (CCT and bootstrap). In Panel B, the ATE increases from 0.037
to 0.051 (CCT) and 0.052 (bootstrap). The confidence intervals tend to shift up
as well.  In contrast to the striking differences between the conventional
and bias-corrected procedures for the mortality estimates, the differences
in Table~\ref{tbl:3} are much smaller.

>>>>

Results from the two robust procedures are similar to each other but greatly
differ from the original estimates. Both ATE estimates are significantly different from
zero and indicate a reduction in mortality, although the confidence intervals are
also very wide, which is likely to be
due to the much smaller bandwidths used relative to the other estimators
($h=3.888$, $b=6.807$). The ATE estimate reported are the bias-corrected
point estimates, and their value indicates that the naive estimates are
subject to substantial bias.

@@

The two robust procedures are again very similar to each other and give
statistically significant, positve, estimates. The confidence intervals tend to shift
relative to the original intervals, increasing both the range of effects consistent
with the data as well as the lower bound on plausible effects.
In contrast to the striking differences between the conventional
and bias-corrected procedures for the mortality estimates, the differences
in Table~\ref{tbl:3} are much smaller.
